---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(my625package.hw3)
library(testthat)
library(bench)
```

To use the function my_lm

```{r}
data(mtcars)
X <- as.matrix(mtcars[, c("wt", "hp")])
y <- mtcars$mpg
result <- fastlm(X, y)
print(result)
```

comparisons against the original R functions to demonstrate both the correctness 

```{r}
test_that("my_lm produces correct results", {
  data(mtcars)
  X <- as.matrix(mtcars[, c("wt", "hp")]) 
  y <- mtcars$mpg

  # using my_lm function
  fastlm_result <- my_lm(X, y)

  # using original R function:lm()
  lm_result <- lm(mpg ~ wt + hp, data = mtcars)

  # compare the coefficients
  expect_true(all.equal(as.numeric(fastlm_result$coefficients),
                        as.numeric(coef(lm_result))))
})

```

test the efficiency of the implemented functions.

```{r}
bench::mark(
  fastlm = as.numeric(fastlm(X, y)$coefficients),
  lm = as.numeric(coef(lm(mpg ~ wt + hp, data = mtcars)))
)
```
To use the function my_lm2

```{r}
# need to source rcpp_lm.cpp first
data(mtcars)
X <- as.matrix(mtcars[, c("wt", "hp")])
y <- mtcars$mpg
result <- my_lm2(X, y)
result
```
comparisons against the original R functions to demonstrate both the correctness 

```{r}
test_that("my_lm2 produces correct results", {
  data(mtcars)
  X <- as.matrix(mtcars[, c("wt", "hp")])
  y <- mtcars$mpg
  # using my_lm2 function
  my_result <- my_lm2(X, y)
  # using original R function:lm()
  lm_result <- lm(mpg ~ wt + hp, data = mtcars)
  # compare the coefficients
  expect_true(all.equal(as.numeric(my_result$coefficients),
                        as.numeric(coef(lm_result))))
})
```

test the efficiency of the implemented function and function before using rcpp

```{r}
# compare with lm() function
bench::mark(
  my_lm = as.numeric(my_lm2(X, y)$coefficients),
  lm = as.numeric(coef(lm(mpg ~ wt + hp, data = mtcars)))
)
# compare with my_lm function
bench::mark(
  my_lm = as.numeric(my_lm2(X, y)$coefficients),
  lm = as.numeric(my_lm(X, y)$coefficients)
)
